\section{Resource plan}
\subsection{Persons}


The following parties are involved in this project: the customer, the sponsor/course leader, the project leaders, the project members, and the supervisors/experts.

The sponsor acts as the customer contact and main project leader. He approves the assignment of project leaders, follows the overall execution of the project plan, and ultimately validates the outcome of the project on behalf of the customer (IFM). He also formulates the project requirements 

The assigned project leaders are responsible for the realization of the given tasks and the coordination of project members. Project leaders are responsible for respecting and 

The project supervisors/experts should be periodically consulted by the project leaders and project members, throughout the duration of the project, primarily in the periods preceding the deadlines for tollgates and milestones.

There is 6 project members who are working on the project\\

Simon Wallin Project manager (PM)\\
Björn Lindström Documents (Doc)\\
Francois Vrel Code Design (CD)\\
Simon Larsson Code Test (CT)\\
Johan Jönsson Code Implementation (CI)\\
Mohammed Rashed Program Operation (PO)\\

The customer, the sponsor/course leader, the project leader and the supervisor/expert is represented by Valeriu Chirita.

\subsection{Work rooms}

The customer IFM provide us with one room (Vakuum room) in Fysikhuset for which we have 2 keys.
The persons responsible for the keys are Simon Wallin and Johan Jönsson.

\subsection{Material}

In the room lent to the project group, we can use:

\begin{itemize}
	\item Software {\&} Hardware Tools
	\item Materials Studio Modelling
	\item Matlab
	\item Dedicated hardware (4 x windows/XP machines) {\&} SUN workstations
	\item White board
\end{itemize}

We also can use any available literature at Linköping University library if needed or find it on the internet.

\subsection{Economy}

There is no funding needed for the project as we can be self sufficient with the material IFM provide us with. The group members will be paid in ECTS credits when the course is finished. The amount of credits given is 7 with implies that the total amount of time spent on this project should be 187h with lectures included.












